---
output: 
  html_document:
    code_folding: hide
    warning: FALSE
---

# DOPD Settlement Model

## Overview

This R script is a reconstruction of 2 Excel-based models which calculate daily payouts for PGE and DO/OKPD in accordance with the XXX agreement.

This script aims to reduce the amount of human interaction needed to run the model with the ultimate goals being (1) a reduction in time spent on the modeling task and (2) preventing potential human error.

This script will have an R Shiny app built on top of it which will enable a user to enter parameters into an easy to use interface and run the model. The model can also be run directly here in R.

## Data

The data used for this model is drawn from data.xlsx. This spreadsheet has the same structure as the original modeling spreadsheet (which has gone through multiple name iterations - Jane will know what the latest version is).

## Notes for developer

Throughout this Rmd there is code that has # MANUALLY ASSIGNED written next to it. These are values that the user will input in manually through the dashboard and will need to have controls on the UI to collect these values.

Remove no longer needed sheets (DG PGE STLMNT, OK PGE STLMNT) from data.xlsx

Make sure model_dependent_accounts vector has ALL possible category names to avoid the script erroring

To add: After user uploads of Excel document, have an initial conditional check to make sure sheet names and column names are correct before even allowing the user to proceed with running to model. Main goal is to mitigate data integration risk (main risk by using an R Script vs. running this script in Excel)

## Section 1: Import libraries and model parameters

#### Import libraries

```{r, warning=FALSE, message=FALSE}

library(tidyverse) # General data wrangling
library(dplyr) # General data wrangling
library(readxl) # Import Excel

```

#### Import parameters shared across both models

```{r}

# Import 'Curves' sheet from within data.xlsx

curves_data <- read_excel('data.xlsx', sheet = "Curves") %>%
  
  # Assign column named "Date" to be Date value types.
  mutate(Date = as.Date(Date, format = "%Y-%m-%d"))

# Import 'SHARES' sheet from within data.xlsx

shares_data <- read_excel('data.xlsx', sheet = 'SHARES')

# Import 'RTDATA' sheet from within data.xlsx

rt_data <- read_excel('data.xlsx', sheet = 'RTDATA') %>%
  
  # Assign column named "time" to be Date value types.
  mutate(time = as.Date(time, format = "%Y-%m-%d"))

```

#### Manually enter parameters shared across both models

These are values that a user will be required to be manually entered through the R Shiny app each time the model is run because this value cannot be extracted from data.xlsx (at least in its current state, this could be changed) and will vary for each run of the model.

These values are parameters for both the DOPD and OKPD model.


```{r}

# Rocky Reach Spill

rrh_spill <- 0 # MANUALLY ASSIGNED

# User selects if today is a trading holiday

is_today_a_trading_holiday <- FALSE # MANUALLY ASSIGNED. Another option would be for the script to decide if it was a holiday, to do that, we'd need a list of all holidays without a year assigned to them

```


#### Manually enter parameters that are unique to DOPD model

```{r}

# The day to run the DOPD model. This will determine what day of pricing for MIDC and POWERDEX will be pulled.
# Dashboard Question: What day do you want to run the DOPD model for?

dopd_flow_date <- as.Date("2023-10-12", format = "%Y-%m-%d") # MANUALLY ASSIGNED

# DOPD's share of Wells Dam on DOPD model run day
# NOTE: CAN BE PULLED IN VIA VLOOKUP FROM 'SHARES' sheet instead of manually entered in the future if desired

dopd_wells_percentage <- 0.2778 # MANUALLY ASSIGNED

# DOPD's share of Rocky Reach Dam on DOPD model run day
# NOTE: CAN BE PULLED IN VIA VLOOKUP FROM 'SHARES' sheet instead of manually entered in the future if desired

dopd_rrh_percentage <- 0.0554 # MANUALLY ASSIGNED


```


#### Manually enter parameters that are unique to OKPD model

Note: These parameters are all currently being entered in manually, but could be pulled via a spreadsheet or function in the future

```{r}

# The day to run the OKPD model. This will determine what day of pricing for MIDC and POWERDEX will be pulled.
# Dashboard Question: What day do you want to run the OKPD model for?

okpd_flow_date <- as.Date("2023-10-12", format = "%Y-%m-%d") # MANUALLY ASSIGNED

# OKPD's share of Rocky Reach Dam on model run day
# NOTE: CAN BE PULLED IN VIA VLOOKUP FROM 'SHARES' sheet instead of manually entered

okpd_rrh_percentage <- 0.0917 # MANUALLY ASSIGNED

```

## Section 2: Run model

#### Set up main dataframe

Set up the main data frame that will be used to calculate the final settlement value and begin by adding in Hours 1 through 24 as well as the MIDC ICE & POWERDEX Prices. 

Corresponding Excel cells from DG PGE STLMNT that are created in this code chunk below -> C36:Z38

```{r}

# Filter curves_data to extract MIDC ICE and POWERDEX Prices

curves_data_filtered <- curves_data %>% filter(Date == dopd_flow_date)

# Create main dataframe for housing model outputs

df <- tibble(
  Hour = 1:24,
  `MIDC ICE Price` = curves_data_filtered$`ICE DA MidC`,
  POWERDEX = curves_data_filtered$`Powerdex MidC`
)

```

#### Build helper functions

There are certain lines of code repeated multiple times throughout the script. This helper function can be used (called) in the future to avoid rewriting code multiple times. This improves readability of the script and efficiency.

```{r}

rt_data_filter <- function (category) {
  rt_data_tidy %>% filter(account == category)
}

```

#### Restructure RTDATA for easier querying.

The way the data in the RTDATA sheet is organized is easy to work with in Excel, but present some challenges for efficient querying in R. This code chunk below restructures RTDATA for easier querying as we will need to pull from it multiple times in subsequent sections.

```{r, warning=FALSE}

##########################
### Tidy RTDATA Sheet ####
##########################

# Create easy-to-query (i.e. "tidy" in R-speak) dataframe
rt_data_tidy <- rt_data %>%
  # Move row value from columns HE01 to the end of the dataframe (HE24) into one column named "Value"
  pivot_longer(cols = `HE01`:ncol(rt_data), names_to = "Hour", values_to = "Value") %>% 
  # Remove HE from Hour names and convert remaining hour number to numeric
  mutate(Hour = as.numeric(sub("^HE", "", Hour)))  %>%
  # Drop any NA values in the Hour column (These are the "Day Total" values)
  filter(!is.na(Hour))

# Conditionally check to make sure rt_data_tidy has all of the needed values under the "accounts" column for the script to run. This will eliminate the need for conditional checks later on.
# If any are missing, add them to the rt_data_tidy df and set values to 0. These will be needed later on for making calculations.

model_dependent_accounts <- c("WEL TOT CAP", "WELLS OBLIGATIONS NET SCHD", "forecast.wells.generation.min-mw", "PART_TOTAL_MAX_CAPACITY_MW-DGLS01", "PART_TOTAL_MIN_CAPACITY-DGLS01", "TOT DG LD MINUS URBN", "DG>OK LL", "DG>CHLN PAL LL", "DG>CHLN RR CEAEA", "BPA>DG PUMP", "DOPD NCW GEN", "AVA>DG LTI", "SENA>DG FRM", "INFLOW_MWH-DGLS01")

# Check for missing accounts and return a vector of missing accounts
missing_accounts <- setdiff(model_dependent_accounts, rt_data_tidy$account)

# Loop through missing accounts
for (account in missing_accounts) {
  # Create a tibble with 24 rows for the missing account
  missing_data <- tibble(
    time = rep(dopd_flow_date, each = 24),
    account = rep(account, each = 24),
    Hour = 1:24,
    Value = rep(0, times = 24)
  )
  
  # Bind the missing account data to rt_tidy_data
  rt_data_tidy <- bind_rows(rt_data_tidy, missing_data)
}

```


#### Calculate Wells Max Values

Calculate Wells Max values following formula from Excel (= DOPD's percentage of Wells * (WEL TOT CAP - WELLS OBLIGATION NET SCHD))

Corresponding Excel cells from DG PGE STLMNT that are created in this code chunk below -> C39:Z39

```{r}

rt_data_wel_tot_cap <- rt_data_filter("WEL TOT CAP")

rt_data_wells_obligations_net_schd <- rt_data_filter("WELLS OBLIGATIONS NET SCHD")

rt_data_wells_max <- 
  # Join WEL TOT CAP and WELLS OBLIGATIONS NET SCHD by Hour
  left_join(rt_data_wel_tot_cap, rt_data_wells_obligations_net_schd, by = "Hour") %>% 
  # Calculate Wells Max (= DOPD's percentage of Wells * (WEL TOT CAP - WELLS OBLIGATION NET SCHD))
  mutate(`Wells Max` = dopd_wells_percentage * (Value.x - Value.y))

# Add Wells Max values to the main df
df <- df %>% mutate(`Wells Max` = rt_data_wells_max$`Wells Max`)
```

#### Calculate Wells Min Values

Calculate Wells Min values following formula from Excel (= DOPD's percentage of Wells * (forecast.wells.generation.min-m - WELLS OBLIGATION NET SCHD))

Corresponding Excel cells from DG PGE STLMNT that are created in this code chunk below -> C41:Z41

```{r}
rt_data_forecast_wells_generation_min_mw <- rt_data_filter("forecast.wells.generation.min-mw")

rt_data_wells_min <- 
  # Join forecast.wells.generation.min-m and WELLS OBLIGATIONS NET SCHD by Hour
  left_join(rt_data_forecast_wells_generation_min_mw, rt_data_wells_obligations_net_schd, by = "Hour") %>% 
  # Calculate Wells Min (= DOPD's percentage of Wells * (forecast.wells.generation.min-mw - WELLS OBLIGATION NET SCHD))
  mutate(`Wells Min` = dopd_wells_percentage * (Value.x - Value.y))

# Add Wells Min values to the main df
df <- df %>% mutate(`Wells Min` = rt_data_wells_min$`Wells Min`)
```

#### Add RRH Max & RRH Min to main df

Corresponding Excel cells from DG PGE STLMNT that are created in this code chunk below -> C42:Z43

EFFICIENCY NOTE: This code is essentially just doing a VLOOKUP and can be made more efficient by bulk transposing.

```{r}

#Filter rt_data_tidy by PART_TOTAL_MIN_CAPACITY-DGLS01
rt_data_part_total_max_capacity <- rt_data_filter("PART_TOTAL_MAX_CAPACITY_MW-DGLS01")

#Filter rt_data_tidy by PART_TOTAL_MIN_CAPACITY-DGLS01
rt_data_part_total_min_capacity <- rt_data_filter("PART_TOTAL_MIN_CAPACITY-DGLS01")

# Add RRH Max values to the main df
df <- df %>% mutate(`RRH Max` = rt_data_part_total_max_capacity$`Value`, 
                    `RRH Min` = rt_data_part_total_min_capacity$`Value`)
```

#### Calculate Load

```{r}

#Filter rt_data_tidy by TOT DG LD MINUS URB
rt_data_tot_dg_ld_minus_urbn <- rt_data_filter("TOT DG LD MINUS URBN")

#Filter rt_data_tidy by DG>OK LL
rt_data_dg_ok_ll <- rt_data_filter("DG>OK LL")

# Filter rt_data_tidy by DG>CHLN PAL LL
rt_data_dg_chln_pal_ll <- rt_data_filter("DG>CHLN PAL LL")

# Merge TOT DG LD MINUS URB, DG>OK LL, DG>CHLN PAL LL into one df and add together to calculate Load
rt_data_load <- rt_data_tot_dg_ld_minus_urbn %>%
  left_join(rt_data_dg_ok_ll, by = "Hour") %>%
  left_join(rt_data_dg_chln_pal_ll, by = "Hour") %>% 
  mutate(Load = Value.x + Value.y + Value)

# Add RRH Max values to the main df
df <- df %>% mutate(Load = rt_data_load$Load)
```

#### Add RRH CEAEA, Pumping Return, 9Canyon

Corresponding Excel cells from DG PGE STLMNT that are created in this code chunk below -> C45:Z47

EFFICIENCY NOTE: This code is essentially just doing a VLOOKUP and can be made more efficient by bulk transposing.

```{r}

#Filter rt_data_tidy by DG>CHLN RR CEAEA
rt_data_dg_chln_rr_ceaea <- rt_data_filter("DG>CHLN RR CEAEA")

#Filter rt_data_tidy by BPA>DG PUMP
rt_data_bpa_dg_pump <- rt_data_filter("BPA>DG PUMP")

#Filter rt_data_tidy by DOPD NCW GEN
rt_data_dopd_ncw_gen <- rt_data_filter("DOPD NCW GEN") %>% 
  mutate(Value = Value * -1)

# Add RRH Max values to the main df
df <- df %>% mutate(`RRH CEAEA` = rt_data_dg_chln_rr_ceaea$`Value`, 
                    `Pumping Return` = rt_data_bpa_dg_pump$`Value`,
                    `9Canyon` = rt_data_dopd_ncw_gen$`Value`)
```

#### Calculate Purchases with Reserves

```{r}

#Filter rt_data_tidy by AVA>DG LTI
rt_data_ava_dg_lti <- rt_data_filter("AVA>DG LTI")

#Filter rt_data_tidy by SENA>DG FRM
rt_data_sena_dg_frm <- rt_data_filter("SENA>DG FRM")

rt_data_purchases_w_reserves <- 
  # Join forecast.wells.generation.min-m and WELLS OBLIGATIONS NET SCHD by Hour
  left_join(rt_data_ava_dg_lti, rt_data_sena_dg_frm, by = "Hour") %>% 
  # Calculate Purchases w/ Reserves (= AVA>DG LTI + SENA>DG FRM)
  mutate(`Purchases w/ Reserves` = Value.x - Value.y)

# Add Purchases w/ Reserves values to the main df
df <- df %>% mutate(`Purchases w/ Reserves` = rt_data_purchases_w_reserves$`Purchases w/ Reserves`)

```

#### Add Purchase for Capacity & Purchase w/o Reserves

EFFICIENCY NOTE: These values can be moved to the top of the script for the user to manually assign. They were added here for 

```{r}

#
purchase_for_capacity <- 0 # MANUALLY ASSIGNED
  
purchase_w_o_reserves <- 0 # MANUALLY ASSIGNED

df <- df %>% 
  mutate(`Purchase for Capacity` = 0, `Purchases w/o Reserves` = 0)

```

#### Calculate Net Load

```{r}
# Add Net Load column to 
df <- df %>% mutate(`Net Load` = Load + `RRH CEAEA` + `Pumping Return` + `9Canyon` + `Purchases w/ Reserves` + `Purchase for Capacity` + `Purchases w/o Reserves`)
```

#### Calculate RRH Gen

```{r}

# Extract Rocky Reach Inflow from RTDATA Tab

rrh_inflow <- rt_data_filter("INFLOW_MWH-DGLS01") %>% select(Value) %>% sum()

print(rrh_inflow)

# Distribute RRH Gen in accordance with the following logic:
# 1. Check if day is weekday/Saturday or Sunday/holiday. If weekday/Saturday, HL and LL will be the same value
# 2. The maximum amount of total generation (rrh_inflow) should be sold during HL hours 7-22
# 3. The amount sold in an individual hour cannot exceed RRH Max for that hour
# 4. The amount sold during each hour should be equal across the 16 hr HL block

# Step 1: Check day of the week

# Check if the day is a Sunday or a Holiday
day_of_week <- weekdays(dopd_flow_date)

if (day_of_week == "Sunday" | is_today_a_trading_holiday == TRUE) {

  # Distribute generation equally across all 24 hours of day
  df <- df %>% 
    mutate(`RRH Gen` = rrh_inflow/24)
  
} else {
  
  # If not a Sunday or Holiday, there are 3 possible scenarios for the distribution
  
  # 1. Low inflow: All values are RRH Min
  # 2. Medium inflow: HL values are above their respective RRH Min values, LL values are RRH Min
  # 3. High inflow: All values are above RRH Min
  
  # Distribute generation across HL hours first. This first step will overcalculate how much RRH Gen will be for these hours. 
  df <- df %>%
    
    # Calculate values for HL hours (7-22)
    mutate(
      
      # Conditionally check if the current row being assessed is between the hours of 7 and 22, inclusive
      `RRH Gen` = ifelse(Hour >= 7 & Hour <= 22,
                      
                       # If TRUE, make the value for that row RRH Max for that hour or total inflow 
                       # divided by 16, whichever is smaller. If FALSE, set value to 0, will be updated later
                       min(min(`RRH Max`), ifelse(rrh_inflow/16 < `RRH Min`, `RRH Min`, rrh_inflow/16)), 0
                       
                       )
          )
    
    # Find how much inflow is left over after this calculation
    rrh_inflow_leftover = rrh_inflow - sum(df$`RRH Gen`[7:22])
    
    # If there is none leftover, we'll need to subtract the total amount of RRH Min needed 
    # to meet the need of hours 1:6 and 23:24 from hours 7:22
    
    if(rrh_inflow_leftover == 0) {
      
      #######################################################
      ####### THIS IS A LOW OR MEDIUM INFLOW SCENARIO #######
      #######################################################
      
      # Step 1: Assign Hours 1:6 and 23:24 to be the same as RRH Min
      df <- df %>%
              mutate(    
                `RRH Gen` = ifelse(Hour %in% c(1:6, 23:24), `RRH Min`, `RRH Gen`)
              )
      
      # Step 2: Find the sum of hours 1:6 and 23:24 RRH Min (now in RRH Gen)
      sum_RRH_LL_hrs <- sum(df$`RRH Gen`[c(1:6, 23:24)])
      
      # Step 3: Subtract the sum of the RHH LL hrs/16 from each RRH gen value during hours 7:22
      df <- df %>%
              mutate(    
                `RRH Gen` = ifelse(Hour >= 7 & Hour <= 22, `RRH Gen` - sum_RRH_LL_hrs/16, `RRH Gen`)
              )
      
      # Step 4: Check to make sure the updated RRH Gen value is now not less than RRH Min. If it is, change it to RRH Min
      df <- df %>%
              mutate(    
                `RRH Gen` = ifelse(Hour >= 7 & Hour <= 22, ifelse(`RRH Gen` < `RRH Min`, `RRH Min`, `RRH Gen`), `RRH Gen`)
              )
    
  } else {
    
    ##############################################
    ####### THIS IS A HIGH INFLOW SCENARIO #######
    ##############################################
    
    df <- df %>%
    mutate(    
      
      # First check that hour in the day is 1:6 or 23:24
      `RRH Gen` = ifelse(Hour %in% c(1:6, 23:24), 
                        
                        # If TRUE, assign value for that row to be the leftover inflow of RRH / 8 or
                        # The lowest value of all that RRH Max values for that time window
                        min(rrh_inflow_leftover / 8, min(c(df$`RRH Max`[1:6], df$`RRH Max`[23:24]))), `RRH Gen`)
    )
  }
  
}

```

#### Short Capacity? Check

```{r}

df <- df %>%
  mutate(`Wells Add` = 0, `PGE SUPPLY CAPACITY` = 0) %>% 
  mutate(`Wells Gen` = pmax(`Wells Min` + `Wells Add`, (`Net Load` + `Wells Add`) - `RRH Gen`, `Wells Add`) + `PGE SUPPLY CAPACITY`) %>% 
  mutate(`Total Gen` = `RRH Gen` + `Wells Gen`) %>% 
  mutate(`Wells Net Max` = `Wells Max` - (.05 * `Load`) - (.05 * (-`9Canyon` + `RRH CEAEA` - `Purchases w/o Reserves` + `Total Gen` - `PGE SUPPLY CAPACITY` * 2))) %>% 
  mutate(`Surplus Capacity - Wells` = `Wells Net Max` - `Wells Gen`)

# Conditional check for Wells surplus capacity during HL hours
if (min(df$`Surplus Capacity - Wells`[7:22]) < 0) {
  
  # If there is surplus capacity, proceed with steps below
  df <- df %>% 
    
    # Set PGE SUPPLY CAPACITY to lowest Surplus Capacity - Wells value during hours 7:22
    mutate(`PGE SUPPLY CAPACITY` = ifelse(Hour >= 7 & Hour <= 22, min(`Surplus Capacity - Wells`), 0)) %>%
    
    # Recalculate Wells Gen with updated PGE SUPPLY CAPACITY values
    mutate(`Wells Gen` = pmax(`Wells Min` + `Wells Add`, (`Net Load` + `Wells Add`) - `RRH Gen`, `Wells Add`) + `PGE SUPPLY CAPACITY`) %>%
    
    # Recalculate Total Gen to account for new Wells Gen value
    mutate(`Total Gen` = `RRH Gen` + `Wells Gen`) %>% 
    
    # Recalculate Wells Net Max to account for updated Total Gen and PGE SUPPLY CAPACITY values
    mutate(`Wells Net Max` = `Wells Max` - (.05 * `Load`) - (.05 * (-`9Canyon` + `RRH CEAEA` - `Purchases w/o Reserves` + `Total Gen` - `PGE SUPPLY CAPACITY` * 2))) %>% 
    
    # Recalculate Surplus Capacity - Wells
    mutate(`Surplus Capacity - Wells` = ifelse(Hour >= 7 & Hour <= 22, `Wells Net Max` - `Wells Gen`, `Surplus Capacity - Wells`))
  
    # After recalculating dependents, if the min of Surplus Capacity is still less than 0, run again
  
    if (min(df$`Surplus Capacity - Wells`[7:22]) < 0) {
    
    # If there is surplus capacity, proceed with steps below
    df <- df %>% 
      
      # Set PGE SUPPLY CAPACITY to lowest Surplus Capacity - Wells value during hours 7:22
      mutate(`PGE SUPPLY CAPACITY` = ifelse(Hour >= 7 & Hour <= 22, `PGE SUPPLY CAPACITY` + min(`Surplus Capacity - Wells`), 0)) %>%
      
      # Recalculate Wells Gen with updated PGE SUPPLY CAPACITY values
      mutate(`Wells Gen` = pmax(`Wells Min` + `Wells Add`, (`Net Load` + `Wells Add`) - `RRH Gen`, `Wells Add`) + `PGE SUPPLY CAPACITY`) %>%
      
      # Recalculate Total Gen to account for new Wells Gen value
      mutate(`Total Gen` = `RRH Gen` + `Wells Gen`) %>% 
      
      # Recalculate Wells Net Max to account for updated Total Gen and PGE SUPPLY CAPACITY values
      mutate(`Wells Net Max` = `Wells Max` - (.05 * `Load`) - (.05 * (-`9Canyon` + `RRH CEAEA` - `Purchases w/o Reserves` + `Total Gen` - `PGE SUPPLY CAPACITY` * 2))) %>% 
      
      # Recalculate Surplus Capacity - Wells
      mutate(`Surplus Capacity - Wells` = ifelse(Hour >= 7 & Hour <= 22, `Wells Net Max` - `Wells Gen`, `Surplus Capacity - Wells`))
  }
}

# Conditional check for Wells surplus capacity during HL hours
if (min(df$`Surplus Capacity - Wells`[c(1:6, 23:24)]) < 0) {
  
  # If there is surplus capacity, proceed with steps below
  df <- df %>% 
    
    # Set PGE SUPPLY CAPACITY to lowest Surplus Capacity - Wells value during hours 7:22
    mutate(`PGE SUPPLY CAPACITY` = ifelse(Hour %in% c(1:6, 23:24), min(`Surplus Capacity - Wells`), 0)) %>%
    
    # Recalculate Wells Gen with updated PGE SUPPLY CAPACITY values
    mutate(`Wells Gen` = pmax(`Wells Min` + `Wells Add`, (`Net Load` + `Wells Add`) - `RRH Gen`, `Wells Add`) + `PGE SUPPLY CAPACITY`) %>%
    
    # Recalculate Total Gen to account for new Wells Gen value
    mutate(`Total Gen` = `RRH Gen` + `Wells Gen`) %>% 
    
    # Recalculate Wells Net Max to account for updated Total Gen and PGE SUPPLY CAPACITY values
    mutate(`Wells Net Max` = `Wells Max` - (.05 * `Load`) - (.05 * (-`9Canyon` + `RRH CEAEA` - `Purchases w/o Reserves` + `Total Gen` - `PGE SUPPLY CAPACITY` * 2))) %>% 
    
    # Recalculate Surplus Capacity - Wells
    mutate(`Surplus Capacity - Wells` = ifelse(Hour %in% c(1:6, 23:24), `Wells Net Max` - `Wells Gen`, `Surplus Capacity - Wells`))
  
    # After recalculating dependents, if the min of Surplus Capacity is still less than 0, run again
  
    if (min(df$`Surplus Capacity - Wells`[c(1:6, 23:24)]) < 0) {
    
    # If there is surplus capacity, proceed with steps below
    df <- df %>% 
      
      # Set PGE SUPPLY CAPACITY to lowest Surplus Capacity - Wells value during hours 7:22
      mutate(`PGE SUPPLY CAPACITY` = ifelse(Hour %in% c(1:6, 23:24), `PGE SUPPLY CAPACITY` + min(`Surplus Capacity - Wells`), 0)) %>%
      
      # Recalculate Wells Gen with updated PGE SUPPLY CAPACITY values
      mutate(`Wells Gen` = pmax(`Wells Min` + `Wells Add`, (`Net Load` + `Wells Add`) - `RRH Gen`, `Wells Add`) + `PGE SUPPLY CAPACITY`) %>%
      
      # Recalculate Total Gen to account for new Wells Gen value
      mutate(`Total Gen` = `RRH Gen` + `Wells Gen`) %>% 
      
      # Recalculate Wells Net Max to account for updated Total Gen and PGE SUPPLY CAPACITY values
      mutate(`Wells Net Max` = `Wells Max` - (.05 * `Load`) - (.05 * (-`9Canyon` + `RRH CEAEA` - `Purchases w/o Reserves` + `Total Gen` - `PGE SUPPLY CAPACITY` * 2))) %>% 
      
      # Recalculate Surplus Capacity - Wells
      mutate(`Surplus Capacity - Wells` = ifelse(Hour %in% c(1:6, 23:24), `Wells Net Max` - `Wells Gen`, `Surplus Capacity - Wells`))
  }
}

```

